### 2015-12-14 PrincipiaMetaphysicaAutomationPart1/doc/document/TheoryOfAbstractObjectsV1.tex
further improvements, various

\isacommand{typedecl}\isamarkupfalse%

@@

\isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%

@@

 based on four constructors: \isa{ERR\ {\isacharprime}a} (identifies erroneous term constructions), \isa{P\ {\isacharprime}a} (identifies 
 propositional formulas), \isa{F\ {\isacharprime}a} (identifies  formulas), and \isa{T\ {\isacharprime}a} (identifies 

@@

\isacommand{datatype}\isamarkupfalse%

@@

\isacommand{abbreviation}\isamarkupfalse%

@@

 \isa{{\isasymA}} ("it is actually the case that"), refer to a (fixed) given world. To model such a 

@@

\isacommand{consts}\isamarkupfalse%

@@

The actuality operator \isa{{\isasymA}} when applied to a formula or propositional formula 

@@

 The compound expression \isa{{\isasymA}\ {\isasymphi}} inherits its syntactical category  \isa{F} (formula) or

@@

 \isa{ERR} (error) or \isa{T} (term), then the syntactical catagory of \isa{{\isasymA}\ {\isasymphi}} 

@@

\isacommand{abbreviation}\isamarkupfalse%
\ {\isasymA}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt\ {\isasymRightarrow}\ io\ opt{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymA}\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline

@@

\isacommand{abbreviation}\isamarkupfalse%
\ Exe{\isadigit{2}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isasymlparr}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isasymrparr}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlparr}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isasymrparr}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isacharparenright}\ of\ \isanewline

@@

\isacommand{abbreviation}\isamarkupfalse%
\ Exe{\isadigit{3}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isasymlparr}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isasymrparr}{\isachardoublequoteclose}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlparr}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isacharcomma}x{\isadigit{3}}{\isasymrparr}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isacharcomma}x{\isadigit{3}}{\isacharparenright}\ of\ \isanewline

@@

\ \ \ \ {\isacharparenleft}F{\isacharparenleft}{\isasymalpha}{\isacharparenright}{\isacharcomma}F{\isacharparenleft}{\isasymbeta}{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ F{\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymalpha}\ w\ {\isasymlongrightarrow}\ {\isasymbeta}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharparenleft}P{\isacharparenleft}{\isasymalpha}{\isacharparenright}{\isacharcomma}P{\isacharparenleft}{\isasymbeta}{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymalpha}\ w\ {\isasymlongrightarrow}\ {\isasymbeta}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}%

@@

\isacommand{abbreviation}\isamarkupfalse%
\ forall{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}{\isacharprime}a{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymforall}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymforall}\ {\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ da{\isacharparenright}\ of\isanewline
\ \ \ \ F{\isacharparenleft}{\isasymphi}{\isacharparenright}\ {\isasymRightarrow}\ F{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isasymforall}x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ F{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ {\isasympsi}\ w{\isacharparenright}\ {\isacharbar}\ P{\isacharparenleft}{\isasymphi}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isasymforall}x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ P{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ {\isasympsi}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ forallBinder{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}{\isacharprime}a{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{binder}\ {\isachardoublequoteopen}\isactrlbold {\isasymforall}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{8}}{\isacharbrackright}\ {\isadigit{9}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymforall}\ x{\isachardot}\ {\isasymphi}\ x\ {\isasymequiv}\ \isactrlbold {\isasymforall}\ {\isasymphi}{\isachardoublequoteclose}\isanewline

@@

\isacommand{abbreviation}\isamarkupfalse%
\ box{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymbox}\ {\isacharunderscore}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{6}}{\isadigit{2}}{\isacharbrackright}\ {\isadigit{6}}{\isadigit{3}}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymbox}{\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline

@@

\isacommand{abbreviation}\isamarkupfalse%
\ lamBinder{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{binder}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{8}}{\isacharbrackright}\ {\isadigit{9}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}\ x{\isachardot}\ {\isasymphi}\ x\ {\isasymequiv}\ \isactrlbold {\isasymlambda}\ {\isasymphi}{\isachardoublequoteclose}\isanewline
\isacommand{abbreviation}\isamarkupfalse%

@@

 \isa{{\isasymiota}{\isacharparenleft}{\isasymlambda}x{\isachardot}{\isasymphi}{\isacharparenright}} to \isa{{\isacharparenleft}THE\ x{\isachardot}\ {\isasymphi}\ cw{\isacharparenright}}, that is Isabelle's inbuilt description operator THE 

@@

\isacommand{abbreviation}\isamarkupfalse%
\ that{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}e\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isasymiota}{\isachardoublequoteclose}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymiota}\ {\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ de{\isacharparenright}\ of\isanewline
\ \ \ \ P{\isacharparenleft}{\isasymphi}{\isacharparenright}\ {\isasymRightarrow}\ T{\isacharparenleft}THE\ x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ P\ {\isasympsi}\ {\isasymRightarrow}\ {\isasympsi}\ cw{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}de{\isacharparenright}{\isachardoublequoteclose}\isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ thatBinder{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}e\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{binder}\ {\isachardoublequoteopen}{\isasymiota}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{8}}{\isacharbrackright}\ {\isadigit{9}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymiota}\ x{\isachardot}\ {\isasymphi}\ x\ {\isasymequiv}\ {\isasymiota}\ {\isasymphi}{\isachardoublequoteclose}%

@@

\ \ \ \ P\ {\isasymphi}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isasymexists}x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ P\ {\isasympsi}\ {\isasymRightarrow}\ {\isasympsi}\ w{\isacharparenright}\ {\isacharbar}\ F\ {\isasymphi}\ {\isasymRightarrow}\ F{\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymexists}x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ F\ {\isasympsi}\ {\isasymRightarrow}\ {\isasympsi}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR\ dio{\isachardoublequoteclose}\ \isanewline
\isacommand{abbreviation}\isamarkupfalse%
\ existsBinder{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}{\isacharprime}a{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{binder}\ {\isachardoublequoteopen}\isactrlbold {\isasymexists}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{8}}{\isacharbrackright}\ {\isadigit{9}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymexists}\ x{\isachardot}\ {\isasymphi}\ x\ {\isasymequiv}\ \isactrlbold {\isasymexists}\ {\isasymphi}{\isachardoublequoteclose}%

@@

\ \ \ \ P{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ if\ {\isasymforall}w{\isachardot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\ {\isasymlongleftrightarrow}\ True\ then\ {\isasymtop}\ else\ {\isasymbottom}\ {\isacharbar}\ F{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ if\ {\isasymforall}w{\isachardot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\ {\isasymlongleftrightarrow}\ True\ then\ {\isasymtop}\ else\ {\isasymbottom}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ {\isacharasterisk}{\isachardoublequoteclose}\isanewline
\isacommand{abbreviation}\isamarkupfalse%

@@

\ \ \ \ P{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ if\ {\isasymexists}w{\isachardot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\ {\isasymlongleftrightarrow}\ True\ then\ {\isasymtop}\ else\ {\isasymbottom}\ {\isacharbar}\ F{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ if\ {\isasymexists}w{\isachardot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\ {\isasymlongleftrightarrow}\ True\ then\ {\isasymtop}\ else\ {\isasymbottom}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ {\isacharasterisk}{\isachardoublequoteclose}\isanewline
\isacommand{abbreviation}\isamarkupfalse%

@@

@@

\isacommand{lemma}\isamarkupfalse%

@@

However, for terms we have%

>>>>

\ \isacommand{typedecl}\isamarkupfalse%

@@

\ \isacommand{type{\isacharunderscore}synonym}\isamarkupfalse%

@@

  based on four constructors: \isa{ERR\ {\isacharprime}a} (identifies erroneous term constructions), \isa{P\ {\isacharprime}a} 
  (identifies propositional formulas), \isa{F\ {\isacharprime}a} (identifies  formulas), and \isa{T\ {\isacharprime}a} (identifies 

@@

\ \isacommand{datatype}\isamarkupfalse%

@@

\ \isacommand{abbreviation}\isamarkupfalse%

@@

  \isa{\isactrlbold {\isasymA}} ("it is actually the case that"), refer to a (fixed) given world. To model such a 

@@

\ \isacommand{consts}\isamarkupfalse%

@@

The actuality operator \isa{\isactrlbold {\isasymA}} when applied to a formula or propositional formula 

@@

  The compound expression \isa{\isactrlbold {\isasymA}{\isasymphi}} inherits its syntactical category  \isa{F} (formula) or

@@

  \isa{ERR} (error) or \isa{T} (term), then the syntactical catagory of \isa{\isactrlbold {\isasymA}{\isasymphi}} 

@@

\ \isacommand{abbreviation}\isamarkupfalse%
\ Actual{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt\ {\isasymRightarrow}\ io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymA}\ {\isacharunderscore}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{6}}{\isadigit{4}}{\isacharbrackright}\ {\isadigit{6}}{\isadigit{5}}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymA}{\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline

@@

\ \isacommand{abbreviation}\isamarkupfalse%
\ Exe{\isadigit{2}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isasymlparr}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isasymrparr}{\isachardoublequoteclose}{\isacharparenright}\ \isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlparr}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isasymrparr}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isacharparenright}\ of\ \isanewline

@@

\ \isacommand{abbreviation}\isamarkupfalse%
\ Exe{\isadigit{3}}{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}e{\isasymRightarrow}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}e\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}{\isasymlparr}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isacharcomma}{\isacharunderscore}{\isasymrparr}{\isachardoublequoteclose}{\isacharparenright}\ \ \isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isasymlparr}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isacharcomma}x{\isadigit{3}}{\isasymrparr}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}{\isacharcomma}x{\isadigit{1}}{\isacharcomma}x{\isadigit{2}}{\isacharcomma}x{\isadigit{3}}{\isacharparenright}\ of\ \isanewline

@@

\ \ \ \ {\isacharparenleft}P{\isacharparenleft}{\isasymalpha}{\isacharparenright}{\isacharcomma}P{\isacharparenleft}{\isasymbeta}{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymalpha}\ w\ {\isasymlongrightarrow}\ {\isasymbeta}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharparenleft}F{\isacharparenleft}{\isasymalpha}{\isacharparenright}{\isacharcomma}F{\isacharparenleft}{\isasymbeta}{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ F{\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymalpha}\ w\ {\isasymlongrightarrow}\ {\isasymbeta}\ w{\isacharparenright}\ {\isacharbar}\ \isanewline
\ \ \ \ {\isacharparenleft}P{\isacharparenleft}{\isasymalpha}{\isacharparenright}{\isacharcomma}F{\isacharparenleft}{\isasymbeta}{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ F{\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymalpha}\ w\ {\isasymlongrightarrow}\ {\isasymbeta}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharparenleft}F{\isacharparenleft}{\isasymalpha}{\isacharparenright}{\isacharcomma}P{\isacharparenleft}{\isasymbeta}{\isacharparenright}{\isacharparenright}\ {\isasymRightarrow}\ F{\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymalpha}\ w\ {\isasymlongrightarrow}\ {\isasymbeta}\ w{\isacharparenright}\ {\isacharbar}\ \isanewline
\ \ \ \ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}%

@@

\ \isacommand{abbreviation}\isamarkupfalse%
\ forall{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}{\isacharprime}a{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymforall}{\isachardoublequoteclose}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymforall}{\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ da{\isacharparenright}\ of\isanewline
\ \ \ \ F{\isacharparenleft}{\isasymphi}{\isacharparenright}\ {\isasymRightarrow}\ F{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isasymforall}x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ F{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ {\isasympsi}\ w{\isacharparenright}\ \isanewline
\ \ {\isacharbar}\ P{\isacharparenleft}{\isasymphi}{\isacharparenright}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isasymforall}x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ P{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ {\isasympsi}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}dio{\isacharparenright}{\isachardoublequoteclose}\isanewline
\ \isacommand{abbreviation}\isamarkupfalse%
\ forallBinder{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}{\isacharprime}a{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{binder}\ {\isachardoublequoteopen}\isactrlbold {\isasymforall}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{8}}{\isacharbrackright}\ {\isadigit{9}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymphi}\ x\ {\isasymequiv}\ \isactrlbold {\isasymforall}\ {\isasymphi}{\isachardoublequoteclose}\isanewline

@@

\ \isacommand{abbreviation}\isamarkupfalse%
\ box{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}io\ opt{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymbox}{\isacharunderscore}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{6}}{\isadigit{2}}{\isacharbrackright}\ {\isadigit{6}}{\isadigit{3}}{\isacharparenright}\ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymbox}{\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ \isanewline

@@

\ \isacommand{abbreviation}\isamarkupfalse%
\ lamBinder{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}{\isacharparenleft}e{\isasymRightarrow}io{\isacharparenright}\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{binder}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{8}}{\isacharbrackright}\ {\isadigit{9}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymlambda}x{\isachardot}\ {\isasymphi}\ x\ {\isasymequiv}\ \isactrlbold {\isasymlambda}\ {\isasymphi}{\isachardoublequoteclose}\isanewline
\ \isacommand{abbreviation}\isamarkupfalse%

@@

  \isa{\isactrlbold {\isasymiota}{\isacharparenleft}{\isasymlambda}x{\isachardot}{\isasymphi}{\isacharparenright}} to \isa{{\isacharparenleft}THE\ x{\isachardot}\ {\isasymphi}\ cw{\isacharparenright}}, that is Isabelle's inbuilt description operator THE 

@@

\ \isacommand{abbreviation}\isamarkupfalse%
\ that{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}e\ opt{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}\isactrlbold {\isasymiota}{\isachardoublequoteclose}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymiota}{\isasymPhi}\ {\isasymequiv}\ case\ {\isacharparenleft}{\isasymPhi}\ de{\isacharparenright}\ of\isanewline
\ \ \ \ F{\isacharparenleft}{\isasymphi}{\isacharparenright}\ {\isasymRightarrow}\ T{\isacharparenleft}THE\ x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ F\ {\isasympsi}\ {\isasymRightarrow}\ {\isasympsi}\ cw{\isacharparenright}\ {\isacharbar}\ P{\isacharparenleft}{\isasymphi}{\isacharparenright}\ {\isasymRightarrow}\ T{\isacharparenleft}THE\ x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ P\ {\isasympsi}\ {\isasymRightarrow}\ {\isasympsi}\ cw{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR{\isacharparenleft}de{\isacharparenright}{\isachardoublequoteclose}\isanewline
\ \isacommand{abbreviation}\isamarkupfalse%
\ thatBinder{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}e{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}e\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{binder}\ {\isachardoublequoteopen}\isactrlbold {\isasymiota}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{8}}{\isacharbrackright}\ {\isadigit{9}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymiota}x{\isachardot}\ {\isasymphi}\ x\ {\isasymequiv}\ \isactrlbold {\isasymiota}\ {\isasymphi}{\isachardoublequoteclose}\isanewline
\ \isacommand{lemma}\isamarkupfalse%
\ \ \ {\isachardoublequoteopen}{\isasymlparr}\ F{\isadigit{1}}\isactrlsup T{\isacharcomma}{\isacharparenleft}\isactrlbold {\isasymiota}x{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}Q{\isadigit{1}}\isactrlsup T{\isasymrbrace}{\isacharparenright}{\isasymrparr}\ {\isacharequal}\ X{\isachardoublequoteclose}%
\ \ %
\isamarkupcmt{X is a propositional formula as intended%

@@

\ \ \ \ P\ {\isasymphi}\ {\isasymRightarrow}\ P{\isacharparenleft}{\isasymlambda}w{\isachardot}{\isasymexists}x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ P\ {\isasympsi}\ {\isasymRightarrow}\ {\isasympsi}\ w{\isacharparenright}\ \isanewline
\ \ {\isacharbar}\ F\ {\isasymphi}\ {\isasymRightarrow}\ F{\isacharparenleft}{\isasymlambda}w{\isachardot}\ {\isasymexists}x{\isachardot}\ case\ {\isacharparenleft}{\isasymPhi}\ x{\isacharparenright}\ of\ F\ {\isasympsi}\ {\isasymRightarrow}\ {\isasympsi}\ w{\isacharparenright}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ ERR\ dio{\isachardoublequoteclose}\ \isanewline
\ \isacommand{abbreviation}\isamarkupfalse%
\ existsBinder{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}{\isacharparenleft}{\isacharprime}a{\isasymRightarrow}io\ opt{\isacharparenright}{\isasymRightarrow}io\ opt{\isachardoublequoteclose}\ {\isacharparenleft}\isakeyword{binder}\ {\isachardoublequoteopen}\isactrlbold {\isasymexists}{\isachardoublequoteclose}\ {\isacharbrackleft}{\isadigit{8}}{\isacharbrackright}\ {\isadigit{9}}{\isacharparenright}\ \ \isakeyword{where}\ {\isachardoublequoteopen}\isactrlbold {\isasymexists}x{\isachardot}\ {\isasymphi}\ x\ {\isasymequiv}\ \isactrlbold {\isasymexists}{\isasymphi}{\isachardoublequoteclose}%

@@

\ \ \ \ P{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ if\ {\isasymforall}w{\isachardot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\ {\isasymlongleftrightarrow}\ True\ then\ {\isasymtop}\ else\ {\isasymbottom}\ \isanewline
\ \ {\isacharbar}\ F{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ if\ {\isasymforall}w{\isachardot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\ {\isasymlongleftrightarrow}\ True\ then\ {\isasymtop}\ else\ {\isasymbottom}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ {\isacharasterisk}{\isachardoublequoteclose}\isanewline
\ \isacommand{abbreviation}\isamarkupfalse%

@@

\ \ \ \ P{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ if\ {\isasymexists}w{\isachardot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\ {\isasymlongleftrightarrow}\ True\ then\ {\isasymtop}\ else\ {\isasymbottom}\ \isanewline
\ \ {\isacharbar}\ F{\isacharparenleft}{\isasympsi}{\isacharparenright}\ {\isasymRightarrow}\ if\ {\isasymexists}w{\isachardot}{\isacharparenleft}{\isasympsi}\ w{\isacharparenright}\ {\isasymlongleftrightarrow}\ True\ then\ {\isasymtop}\ else\ {\isasymbottom}\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ {\isacharasterisk}{\isachardoublequoteclose}\isanewline
\ \isacommand{abbreviation}\isamarkupfalse%

@@

Question: What are the next two lemmata expected to return? So far they return truth. If that should
  be disabled (in the definition of implication), the  we might run into a problem with the definition 
  of \isa{x\ \isactrlbold {\isacharequal}\isactrlsub E\ y} below. Discuss.%
\ \isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}\ \isactrlbold {\isasymrightarrow}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%
\ \isacommand{lemma}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}\isactrlbold {\isasymforall}x{\isachardot}\ {\isasymlbrace}x\isactrlsup T{\isacharcomma}R\isactrlsup T{\isasymrbrace}\ \isactrlbold {\isasymrightarrow}\ {\isasymlparr}R\isactrlsup T{\isacharcomma}x\isactrlsup T{\isasymrparr}{\isacharparenright}{\isacharbrackright}\ {\isacharequal}\ {\isasymtop}{\isachardoublequoteclose}%

@@

\ \isacommand{lemma}\isamarkupfalse%

@@

However, for terms we have:%
\ \isacommand{lemma}\isamarkupfalse%
